Regularization Techniques for PSF--Matching Kernels. II. Pre--Filtering of Input Images

### 2015-02-24 submit/ms.tex
Minor wording/ref fixes

The detection of transient objects or known--object variability in uncrowded fields may be undertaken at the catalog level \cite[e.g.]{}{2009ApJ...696..870D}.
However, when searching for variability in regions where there is significant confusion, catalog--based methods become heavily dependent on how objects are deblended, which itself is typically a function of the image resolution (or seeing).
For this reason, image subtraction techniques have been developed that perform the subtraction of a prior imaging epoch from a newly acquired one, subtracting out all static sources and only leaving signatures of objects that have changed in position or brightness in a ``difference image''.
By reducing the number of objects to measure, these variable sources may be uniquely photometered without significant deblending issues \citep[however, crowded difference images with spatially overlapping variable sources are possible, e.g.][]{1996ApJ...473L..87C}.
This technique is highly advantageous for the study of variability in the Galactic bulge \citep[e.g. microlensing;][]{1999ApJ...521..602A}, nearby galaxies \citep[e.g. nearby supernovae;][]{2011Natur.480..344N}, or for the study of nuclear variability in more distant galaxies \cite[e.g.][]{2014ApJ...782...37C}.
When used, image subtraction is typically applied to the entirety a time--domain dataset, in both sparse and crowded fields, so as to have a consistent treatment of all of the data.

@@

A key recognition of recent surveys is that systematic effects (i.e. non--astrophysical variability) dominate the population of objects found in difference images \citep{2008AJ....135..348S,2013PASP..125..357D}.
This has opened the door for the at--scale adoption of machine--learning (ML) techniques to separate the true transients from the false detections\footnote{In binary classification, sources of contamination are referred to as ``false positives''.  However, since ``positive'' also may refer to the polarity of a difference image detection, and we indeed accept both positive--going and negative--going detections as ``false positives'', we use the term ``false detections'' here to refer to these sources.}\citep{2012PASP..124.1175B,2015arXiv150105470W}.
This work is encouraging, with recent single--band random--forest--based ML suites having 98--99\% classification efficiency at 95\% sample purity for specific classes of variability \citep{2011ApJ...733...10R}.
However, overall misclassification rates across all sources are of order 10--20\%.
For LSST this technology must be improved to include multi--band information \cite[e.g.][]{2015arXiv150101314K}, and meet the requirements of 90\% completeness and 95\% purity at the 6--sigma detection threshold, for the nightly real--time alert stream (per LSST Observatory System Specifications).
A necessary step towards achieving this goal is to understand the sources of false detections in images, and to develop new techniques to avoid generating or reporting them.
We describe such a novel algorithm here, which involves regularizing the PSF--matching operation by smoothing the science image with its own PSF.
As we will demonstrate, this is not an arbitrary decision, but merely re--orders an operation that occurs naturally in the process of difference image source detection.
By moving this operation earlier in the pipeline in a manner that commutes with the standard technique, we introduce no new pixel--level operations into the processing, while simultaneously reducing our sensitivity to systematic effects due to ``sharpening'', or deconvolution, during PSF--matching.

@@

\begin{table*}[t]
\centering
\begin{tabular}{ccc}
\hline
\multicolumn{3}{|c|}{Variance Ratios: $D'_{post} / D'_{pre}$} \\
\hline
Visit    & Empirical & Propagated \\
\hline
v6866601 & $1.011 \pm 0.016$    & $1.710 \pm 0.049$    \\
v6866602 & $1.001 \pm 0.001$    & $0.967 \pm 0.001$    \\
v6866603 & $1.002 \pm 0.001$    & $0.974 \pm 0.002$    \\
\end{tabular}
\caption{{\rm This inter--image comparison shows the ratios of the variance planes at the detection stage (i.e. in image $D'$).
  Ratios are in the sense of the variance of the post--filtered image divided by the variance of the pre--filtered image.
  The first column represents the ratios of the empirical variance, as derived from the image--plane pixels.
  The second column reports the ratios of the medians of the propagated variance planes.
  We report the mean and RMS across all sensors.
\label{tab-variance2}}}
\end{table*}

>>>>

The detection of transient objects or known--object variability in uncrowded fields may be undertaken at the catalog level \cite[e.g.][]{2009ApJ...696..870D}.
However, when searching for variability in regions where there is significant confusion, catalog--based methods become heavily dependent on how objects are deblended, which itself is typically a function of the image resolution (or seeing).
For this reason, image subtraction techniques have been developed that perform the subtraction of a prior imaging epoch from a newly acquired one, subtracting out all static sources and only leaving signatures of objects that have changed in position or brightness in a ``difference image''.
By reducing the number of objects to measure, these variable sources may be uniquely photometered without significant deblending issues \citep[however, crowded difference images with spatially overlapping variable sources are possible, e.g.][]{1996ApJ...473L..87C}.
This technique is highly advantageous for the study of variability in the Galactic bulge \citep[e.g. microlensing;][]{1999ApJ...521..602A}, nearby galaxies \citep[e.g. nearby supernovae;][]{2011Natur.480..344N}, or for the study of nuclear variability in more distant galaxies \cite[e.g.][]{2014ApJ...782...37C}.
When used, image subtraction is typically applied to the entirety a time--domain dataset, in both sparse and crowded fields, so as to have a consistent treatment of all of the data.

@@

A key recognition of recent surveys is that systematic effects (i.e. non--astrophysical variability) dominate the population of objects found in difference images \citep{2008AJ....135..348S,2013PASP..125..357D}.
This has opened the door for the at--scale adoption of machine--learning (ML) techniques to separate the true transients from the false detections\footnote{In binary classification, sources of contamination are referred to as ``false positives''.  However, since ``positive'' also may refer to the polarity of a difference image detection, and we indeed accept both positive--going and negative--going detections as ``false positives'', we use the term ``false detections'' here to refer to these sources.}\citep{2012PASP..124.1175B,2015arXiv150105470W}.
This work is encouraging, with recent single--band random--forest--based ML suites having 98--99\% classification efficiency at 95\% sample purity for specific classes of variability \citep{2011ApJ...733...10R}.
{\bf IS THIS REAL VS BOGUS?}
However, overall misclassification rates across all sources are of order 10--20\%.
For LSST this technology must be improved to include multi--band information \cite[e.g.][]{2015arXiv150101314K}, and meet the requirements of 90\% completeness and 95\% purity at the 6--sigma detection threshold, for the nightly real--time alert stream (per LSST Observatory System Specifications).
A necessary step towards achieving this goal is to understand the sources of false detections in images, and to develop new techniques to avoid generating or reporting them.
We describe such a novel algorithm here, which involves regularizing the PSF--matching operation by smoothing the science image with its own PSF.
As we will demonstrate, this is not an arbitrary decision, but merely re--orders an operation that occurs naturally in the process of difference image source detection.
By moving this operation earlier in the pipeline in a manner that commutes with the standard technique, we introduce no new pixel--level operations into the processing, while simultaneously reducing our sensitivity to systematic effects due to ``sharpening'', or deconvolution, during PSF--matching.

@@

\begin{table*}[t]
\centering
\begin{tabular}{ccc}
\hline
\multicolumn{3}{|c|}{Variance Ratios: $D'_{post} / D'_{pre}$} \\
\hline
Visit    & Empirical & Propagated \\
\hline
v6866601 & $1.011 \pm 0.016$    & $1.710 \pm 0.049$    \\
v6866602 & $1.001 \pm 0.001$    & $0.967 \pm 0.001$    \\
v6866603 & $1.002 \pm 0.001$    & $0.974 \pm 0.002$    \\
\end{tabular}
\caption{{\rm This inter--image comparison shows the ratios of the variance planes between $D'_{post}$ and $D'_{pre}$ (i.e. at the detection stage).
  Ratios are in the sense of the variance of the post--filtered image divided by the variance of the pre--filtered image.
  The first column represents the ratios of the empirical variance, as derived from the image--plane pixels.
  The second column reports the ratios of the medians of the propagated variance planes.
  We report the mean and RMS across all sensors.
\label{tab-variance2}}}
\end{table*}
